The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-08-29 manuscript.Rmd
[fix #58] include global estimate for fraction of species barcoded

<!-- add overall mean number before getting into details -->
The proportion of species within the US EEZ that have DNA barcodes varies from `r format_output(stat_barcoding$min_eez_value * 100)`% for `r stat_barcoding$min_eez_phylum` to `r format_output(stat_barcoding$max_eez_value * 100)`% for `r stat_barcoding$max_eez_phylum` (Fig. \@ref(fig:proportion-barcoded)). The GOM has comparable coverage than for the EEZ, while the PNW is better barcoded with >30% species-level coverage across each of the five most diverse phyla. This is driven in part by the active Canadian barcoding effort in British Columbia. In 2012, it was estimated that, at a global scale, less than 3% of the marine species had been sequenced [@Appeltans2012], and that this number was even lower in some areas (e.g. 2.6% for the Antarctic [@Grant2009]). Thus the US fauna is generally better characterized than other parts of the world.

>>>>

<!-- add overall mean number before getting into details -->

The marine invertebrates of the US have generally been characterized genetically at a higher level than other parts of the world: `r format_output(prop_spp_barcoded$p_barcoded * 100)`% (n = `r format(nrow(combined_species), big.mark=",")`) of the fauna has DNA barcodes available.  In 2012, it was estimated that, at a global scale, less than 3% of the marine species had been sequenced [@Appeltans2012], and that this number was even lower in some areas (e.g., 2.6% for the Antarctic [@Grant2009]).  This proportion varies by phylum from `r format_output(stat_barcoding$min_eez_value * 100)`% for `r stat_barcoding$min_eez_phylum` to `r format_output(stat_barcoding$max_eez_value * 100)`% for `r stat_barcoding$max_eez_phylum` (Fig. \@ref(fig:proportion-barcoded)). The GOM has comparable coverage than for the EEZ, while the PNW is better barcoded with >30% species-level coverage across each of the five most diverse phyla. This is driven in part by the active Canadian barcoding effort in British Columbia.
